\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
  \textbf{\Huge \scshape Aliif Arief Maulana} \\ \vspace{1pt}
  \small +6285172054903 $|$ \href{mailto:me@aliifam.com}{\underline{me@aliifam.com}} $|$
  \href{https://linkedin.com/in/aliif}{\underline{linkedin.com/in/aliif}} $|$
  \href{https://github.com/aliifam}{\underline{github.com/aliifam}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Universitas Gadjah Mada}{Yogyakarta, Indonesia}{B.A.Sc in Software Engineering Technology, GPA: 3.8/4.0}{Aug 2021 -- Aug 2025}
\resumeSubheading{SMAIT Al-Kahfi}{Bogor, Indonesia}{Science Major}{Jul 2018 -- Jun 2021}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Full-stack Developer}{Jan 2025 -- Present}{PT. Horus Technology}{Yogyakarta, Indonesia}
\resumeItemListStart
\resumeItem{Developed and maintained web platforms including Tamu.id, Indorobotik.com, and Ramasakti integrations.}
\resumeItem{Built REST APIs using Python, frontend using Vue.js, CI/CD with GitLab CI, and deployed on GCP.}
\resumeItem{Handled complete rewrite of Tamu.id v2 focusing on offline fault tolerance and IoT integration.}
\resumeItemListEnd

\resumeSubheading{Back End Developer (Intern)}{Sep 2024 -- Dec 2024}{PT. Cobra Dental Indonesia}{Yogyakarta, Indonesia}
\resumeItemListStart
\resumeItem{Built ReactJS-based frontend dashboard and REST APIs using Laravel.}
\resumeItem{Maintained and improved legacy systems.}
\resumeItemListEnd

\resumeSubheading{Cloud Computing Student}{Aug 2023 -- Jan 2024}{Bangkit Academy by Google, Gojek, Tokopedia, Traveloka}{Remote}
\resumeItemListStart
\resumeItem{Completed Google Cloud Professional Learning Path.}
\resumeItem{Deployed backend services with GCP: Compute Engine, App Engine, Cloud SQL, Cloud Run.}
\resumeItem{Top 10\% graduate out of 47,800 applicants. (Distinction Graduate)}
\resumeItemListEnd

\resumeSubheading{Fullstack Developer (Intern)}{Dec 2022 -- Apr 2023}{PT Aino Indonesia}{Yogyakarta, Indonesia}
\resumeItemListStart
\resumeItem{Refactored legacy code for better maintainability.}
\resumeItem{Handled database transaction/locking issues, improved CI/CD and image load performance using 3rd-party CDN API.}
\resumeItemListEnd

\resumeSubheading{Teaching Assistant - Database System}{Feb 2023 -- Jun 2023}{Universitas Gadjah Mada}{Yogyakarta, Indonesia}
\resumeItemListStart
\resumeItem{Assisted in teaching database fundamentals, supporting lab sessions, and grading.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Tamu.id V2} $|$ Flask, Vue.js, PostgreSQL, GitLab CI, GCP}{Mar 2025 -- Present}
\resumeItemListStart
\resumeItem{Full rewrite from V1 with breaking changes to support offline IoT integration and fault tolerance.}
\resumeItem{Implemented secure OTP-based authentication and data syncing mechanism.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{SIKPonpes} $|$ Laravel, MySQL}{Jun 2023 -- Dec 2023}
\resumeItemListStart
\resumeItem{Built a financial information system for Islamic boarding school operations.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Indorobotik Spinning Gacha} $|$ Vue.js, Flask}{Feb 2025 -- Mar 2025}
\resumeItemListStart
\resumeItem{Gamified loyalty program with wheel-spin prize logic integrated with customer account.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Certifications}
\resumeSubHeadingListStart
\resumeSubheading{Google Cloud Associate Cloud Engineer}{Feb 2024}{Credential ID: 93865145}{Expires Feb 2027}
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \textbf{Languages:} PHP, Python, JavaScript, SQL, HTML/CSS, TypeScript
  \item \textbf{Frameworks:} Flask, Laravel, Vue.js, React.js, FastAPI, Express.js, Nest.js
  \item \textbf{Databases:} PostgreSQL, MySQL, SQLite, MongoDB
  \item \textbf{DevOps:} Git, GitLab CI/CD, Docker, Google Cloud Platform (GCP)
  \item \textbf{Tools:} VS Code, Postman, DBeaver, Linux Terminal
\end{itemize}

\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item Indonesian: Native proficiency
  \item English: Limited working proficiency
  \item Arabic: Elementary proficiency
\end{itemize}

\end{document}
